Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-03-31 modeling-volunteer-computing-gecco.tex
Ack'ing previous paper

\section{Materials: running an island model in the browser}
\label{sec:exp}

@@

The server was also written using node.js and the {\tt express.js}
module and has three REST \cite{Castillo12REST} %FERGU: cito a este
                                %paper que es un cap√≠tulo de libro en
                                %vez de Arxiv
% OK - JJ
functions, that is, three functions that can be accessed from any
client, including the browser, via a request encoded in an URL and a
standard HTTP command. These functions are\begin{itemize}
\item {\tt GET random} returns a random, non-evaluated individual,
  from the pool. The pool is just an array containing chromosomes,
  that is initialized at the beginning of the experiment.
\item {\tt PUT one} puts a single individual along with its fitness in the pool. In REST
  conventions, {\tt PUT} is used to create a resource, that is why it
  is used, in this case, to add a new individual to the pool.
\end{itemize}

In fact, the program includes more logic to serve the static pages
that contain the talk in which it is included and the JavaScript/CSS
code also, but it all amounts to a small amount of code. This code can
be deployed, in principle, in any server running node.js, but for the
purposes of this experiment Heroku, a Platform as a Service with a
free tier, has been chosen. It could be also be deployed, with small
or no modification, to OpenShift or other similar PaaS. Far from being
a freeriding way, using free or very low cost servers can be a
sustainable way of performing massive distributed evolutionary
computation experiments \cite{Merelo2014,jj:idc:lowcost}.

>>>>

\section{An island model in the browser}
\label{sec:exp}

@@

The server, that was also introduced during \cite{arxiv:modeling}, has
been rewritten in part to add new features that make experimentation
easier. I has been written using node.js and the {\tt express.js}
module and includes the following REST \cite{Castillo12REST} 
routes:
\item {\tt GET random} returns a random, non-evaluated individual,
  from the pool. The pool is just an array containing chromosomes,
  that is initialized at the beginning of the experiment.
\item {\tt PUT one} puts a single individual along with its fitness in the pool. In REST
  conventions, {\tt PUT} is used to create a resource, that is why it
  is used, in this case, to add a new individual to the pool.
\end{itemize}

These two routes are, in fact, an universal interface that can be
accessed from any program, written in any language that can connect
via HTTP.

The server program includes more logic to serve the static pages
that contain the talk in which it is included and the JavaScript/CSS
code also, but it all amounts to a small amount of code. This code can
be deployed, in principle, in any server running node.js, but for the
purposes of this experiment Heroku, a Platform as a Service with a
free tier, has been chosen. It could be also be deployed, with small
or no modification, to OpenShift or other similar PaaS. Far from being
a freeriding way, using free or very low cost servers can be a
sustainable way of performing massive distributed evolutionary
computation experiments \cite{Merelo2014,jj:idc:lowcost}.
